---
title: "EPM analysis auto vs manual"
author: "David Fuentes"
always_allow_html: yes
date: "`r Sys.Date()`"
output:
  html_document:
    theme: united
    toc: yes
    toc_collapsed: yes
    toc_float: yes
---
Usage: Rscript -e " rmarkdown::render( 'automanualepm.Rmd', output_file = './automanualepm.html' )"
Usage: R; rmarkdown::render( 'automanualepm.Rmd', output_file = './automanualepm.html' )

EPM analysis corresponding to https://arxiv.org/abs/2309.03980

address review comments for mask sensitivity
```{r setup, include=FALSE}
#install.packages('plotly') 
library(htmltools)
library(plotly)
options(width=135)
```
 
# Load Data

Note that some manual labels were missing that causes epm =0 downstream. Dropping these for now.
```{r Load data}
manualdataset <- read.csv( "epmstats/widejoin.csv", na.strings=c(".", "NA", "", "?"), strip.white=TRUE, encoding="UTF-8")
autodataset   <- read.csv("autostats/widejoin.csv", na.strings=c(".", "NA", "", "?"), strip.white=TRUE, encoding="UTF-8")
epmmanualsubset  <- subset(manualdataset, FeatureID == 'epm' & LabelID> 0 & Mean > 0 )  
epmautosubset    <- subset(autodataset  , FeatureID == 'epm' & LabelID> 0 )
```
# merge data frames 

UID encodes patient id and time point
LabelID is the ROI label

```{r merge}
automanualdata = merge(x = epmmanualsubset , y = epmautosubset  , by = c("UID","LabelID"),suffixes=c("man","aut"))
#cbind(as.character(automanualdata$UID),automanualdata$LabelID,automanualdata$Meanman,automanualdata$Meanaut)
```

# analyze

plot and compute correlation

```{r analyze}
#make the main plot
plot(automanualdata$Meanman,automanualdata$Meanaut)

#add linear trend
abline(lm(automanualdata$Meanaut~automanualdata$Meanman))

#compute trend line
m1 = lm(automanualdata$Meanman~automanualdata$Meanaut)
line.fmt = list(dash="solid", width = 1.5, color=NULL)

fig <- plot_ly(
  automanualdata, x = ~Meanman, y = ~Meanaut,type="scatter",
  # Hover text:
  text = ~paste("UID: ", UID, '<br>LabelID:', LabelID)
  #color = ~carat, size = ~carat
) # %>% add_trace(automanualdata,x = ~Meanman, y = predict(m1), mode = "lines")

#fig = add_lines(fig, x=myxi , y=predict(m1), line=line.fmt, name="Linear")
fig = layout(fig,xaxis = list(title = 'Manual'), yaxis = list(title = 'Automatic'))

fig

# Pearson correlation between 2 variables
cor(automanualdata$Meanman ,automanualdata$Meanaut)
```
